### 2019-03-23 reports/thesis/chapters/5_inference.tex
Relocate inference figures

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMean}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidStd}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMixtureMean}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidMixtureStd}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_mean}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_var}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_kurtosis}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_mean}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_var}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_kurtosis}
\end{figure}

@@

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
\end{figure}

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius  Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMean}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidStd}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMixtureMean}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidMixtureStd}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_mean}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_var}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_kurtosis}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_mean}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_var}
\end{figure}

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_kurtosis}
\end{figure}

@@

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0Empirical_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the 100 repeats of the experiment.}
\end{figure}

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDust0MadMode_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius  Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the 100 repeats of the experiment.}
\end{figure}

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before/after contamination and after filtering. In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination. The filter used a kernel radius . Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The FDR was controlled at the 5\% level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustMadMode_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before/after contamination and after filtering. In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination. The filter used a kernel radius . Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The FDR was controlled at the 5\% level. The box plot summarise the 100 repeats of the experiment.}
\end{figure}
